### 2015-08-11 whoop.tex
Added references to web pages

\noindent\textbf{Architecture }
%
Fig.~\ref{fig:whoop} depicts the \whoop toolchain. The input to \whoop is a Linux driver written in C, together with an environmental model\footnote{This consists of stub header files modeling relevant Linux kernel APIs.} that is required to ``close'' the driver so that it can be analyzed for races. Initially, \whoop uses three LLVM-based tools~\cite{lattner2004llvm}, Chauffeur, Clang and SMACK~\cite{rakamaric2014smack}, to translate the driver and its environmental model into an abstract program written in the Boogie intermediate verification language (IVL)~\cite{deline2005boogiepl}.  Boogie is a simple imperative language with well-defined semantics that is used as the input to a number of cutting-edge verifiers (e.g.\ the Boogie verifier and \corral). Next, \whoop instruments and sequentializes the program to perform symbolic pairwise lockset analysis (see Fig.~\ref{fig:whoop}--B and \S\ref{sec:symbolicpairwise}) using the Boogie verification engine. After the verification phase ends, \whoop can exploit any inferred race-freedom guarantees to accelerate precise race-checking with \corral (see Fig.~\ref{fig:whoop}--C and \S\ref{corral}).

>>>>

\noindent\textbf{Architecture }
%
Fig.~\ref{fig:whoop} depicts the \whoop toolchain. The input to \whoop is a Linux driver written in C, together with an environmental model\footnote{This consists of stub header files modeling relevant Linux kernel APIs.} that is required to ``close'' the driver so that it can be analyzed for races. Initially, \whoop uses three LLVM-based tools~\cite{lattner2004llvm,llvm}, Chauffeur, Clang~\cite{clang}, and SMACK~\cite{rakamaric2014smack,smack}, to translate the driver and its environmental model into an abstract program written in the Boogie intermediate verification language (IVL)~\cite{deline2005boogiepl}.  Boogie is a simple imperative language with well-defined semantics that is used as the input to a number of cutting-edge verifiers (e.g.\ the Boogie verifier and \corral). Next, \whoop instruments and sequentializes the program to perform symbolic pairwise lockset analysis (see Fig.~\ref{fig:whoop}--B and \S\ref{sec:symbolicpairwise}) using the Boogie verification engine. After the verification phase ends, \whoop can exploit any inferred race-freedom guarantees to accelerate precise race-checking with \corral (see Fig.~\ref{fig:whoop}--C and \S\ref{corral}).
